

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\classesList}[4]{
	\item\small{
		{#1 #2 #3 #4 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textbf{\small #2} \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & \textbf{\small #2}\\
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%

\begin{document}
	
	
	\begin{center}
		{\Huge \scshape Sebastian G\u albini\c t\u a } \\ \vspace{1pt}
		12 Street Prieteniei, Bac\u au, Bac\u au \\ \vspace{1pt}
		\small \raisebox{-0.1\height}\faPhone\ 0740918796 ~ \href{mailto:sebastian.galbinita97@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sebastian.galbinita97@gmail.com}} ~ 
		\href{https://linkedin.com/in/galbinita-sebastian}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com}}  ~
		\href{https://github.com/GalbinitaSebastian97}{\raisebox{-0.2\height}\faGithub\ \underline{github.com}}
		\vspace{-8pt}
	\end{center}
	
	
	%-----------EDUCATION-----------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{\href{https://github.com/GalbinitaSebastian97/CV-LaTeX-/tree/main/Acts/Faculty}{„Alexandru Ioan Cuza” University of Ia\c si}}{Sep. 2017 -- Sep. 2020}
	{Bachelor degree in Mathematics with a specialization in Mathematics and Computer Science.}{Ia\c si, Ia\c si}
	\begin{itemize}[itemsep=-5pt, parsep=6pt]
		\item\small My scientific paper is entitled as \href{https://github.com/GalbinitaSebastian97/Licenta-2017-2020/blob/master/Licenta/licentaa.pdf}{"Algorithms for graphs and applications"}. 	
	\end{itemize}
	\resumeSubheading
	{„Gheorghe Vr\u anceanu” National College of Bac\u au}{Sep. 2013 -- July 2017}
	{High school diploma with a specialization in Mathematics and Computer Science.}{Bac\u au, Bac\u au}
	\resumeSubHeadingListEnd
	
	%------RELEVANT COURSEWORK-------
	\section{Relevant Coursework}
	%\resumeSubHeadingListStart
	\begin{multicols}{3}
		\begin{itemize}[itemsep=-5pt, parsep=6pt]
			\item\small Data Structures
			\item Algorithms Analysis
			\item Database Management
			\item Advanced Programming Techniques
			\item API
			\item MVC

		\end{itemize}
	\end{multicols}
	\vspace*{2.0\multicolsep}
	%\resumeSubHeadingListEnd
	
	
	%-----------EXPERIENCE-----------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Continental}{November 2019 -- December 2019}
	{Junior Programmer}{Ia\c si, Ia\c si}
	\resumeItemListStart
	\resumeItem{For this internship my task was to create a project with a GUI interface in Raspberry using Python. The tasks that I had to implement varied from changing the lights of the vehicle to the client's preferences to having a login system and sending encrypted codes to the server. The assets that I have learned during my internship:}
	\subitem{ - Weekly meetings that we discussed the tasks that we finished which helped me improve my programming and communication skills.}
	\subitem{ - Had the opportunity to develop my first python project that greatly contributed on how to think a program should be constructed. }
	\resumeItemListEnd
	
	\resumeSubheading
	{Pentalog}{March 2020 -- April 2020}
	{Junior Programmer}{Ia\c si, Ia\c si}
	\resumeItemListStart
	\resumeItem{The task that I was given was to create a virtual storage with no interface in Java. By storing the data in a text file I had to read it and operate all the CRUD operations. Skills that I have learned:}
	\subitem{ - Code reviews with my mentor that helped to improve the readability and functionality of my code.}
	\subitem{ - Discussions with my colleagues about the data structures ideal for this project and the implementation of it.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-16pt}
	
	%-----------PROJECTS-----------
	\section{Projects}
	\vspace{-5pt}
	\resumeSubHeadingListStart
	\resumeProjectHeading
	{\textbf{\href{https://github.com/GalbinitaSebastian97/MiniGPS}{Mini-GPS}} $|$ \emph{C++, Graphs, Shortest Path}}{September 2020}
	\resumeItemListStart
	\resumeItem{ The Mini-GPS application is based on Dijkstra's algorithm. The project illustrates a simple GPS model, displaying 3 different routes between the source and destination. The project produces an offline version of a GPS in which there are no real-time data on the current coordinates of the driver. }
	\resumeItemListEnd
	\vspace{-13pt}
	\resumeProjectHeading
	{\textbf{\href{https://github.com/GalbinitaSebastian97/API}{API}} $|$ \emph{Python, SQL}}{October 2021}
	\resumeItemListStart
	\resumeItem{The goal of this project was to create an API from scratch and exploring different techniques of implementing all the CRUD operations. The client can send requests to the server and if they are valid, send the resource that they want.}
	\resumeItemListEnd 

	\resumeSubHeadingListEnd
	\vspace{-15pt}
	
	
	%
	%-----------PROGRAMMING SKILLS-----------
	\section{Technical Skills}
	\begin{itemize}[leftmargin=0.15in, label={}]
		\small{\item{
				\textbf{Languages}{: Python, HTML/CSS, MATLAB, C++11.} \\
				\textbf{Developer Tools}{: VS Code, Atom, Postman, PostgreSQL, TeXstudio .} \\
				\textbf{Development Environment}{: Linux, GitHub, Mac.} \\
		}}
	\end{itemize}
	\vspace{-16pt}
	
	
	%-----------INVOLVEMENT---------------
	\section{Language}
	\resumeSubHeadingListStart
	\resumeSubSubheading{English}{September 2021 -- Present}
	\resumeItemListStart
	\resumeItem{Cambridge C1 Advanced \href{https://github.com/GalbinitaSebastian97/CV-LaTeX-/blob/main/Acts/Cambridge/Cambridge.jpeg}{(Certificate in Advanced English)}.}
	\resumeItemListEnd
	\resumeSubSubheading{Romanian}{Present}
	\resumeItemListStart
	\resumeItem{Native Language.}
	\resumeItemListEnd
	\resumeSubHeadingListEnd
	
	\begin{center}
	\tiny This CV was developed in TeXstudio using LaTeX. 
	
	\tiny For the code, check out my \href{https://github.com/GalbinitaSebastian97/CV-LaTeX-/blob/main/CV/CV.tex}{\underline{repo}} on github.
	\end{center}
	
\end{document}